Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-10-14 xrb/paper.tex
Updates to 1D plots and speedplot
Also made some edits to the flame properties section.

To understand the time and length scales involved in flame
propagation, we do a 1D simulation of a laminar flame using our
microphysics.  Figure~\ref{fig:flame} shows the flame properties for a 
% \AssignTo{Kiran and Mike will remake with the 10/10 boosted flame}
He flame using the standard conductivities and our simple reaction
network.  This flame had a density of $2\times 10^6~\gcc$ and 
% \MarginPar{double check}
temperature of $5\times 10^7$~K.  We note that this flame speed is
about $2\times 10^4~\cms$, the flame width is about 20~cm, and it
takes about 0.1~s to settle into a sustained flame.  Note this speed
is quite small compared to the speed estimated in
\citet{spitkovsky2002}.  We expected a multidimensional flame to
accelerate due to hydrodynamics interactions (wrinkling, turbulence
interactions, directed flows feeding fuel into the flame, ...).

\begin{figure*}[t]
\plottwo{flame}{speed}
\caption{\label{fig:flame} Our ``standard'' flame.}
\end{figure*}

@@

Flame properties are show in Table XX \MarginPar{we'll redo the table with 10/10 and 5/5/ and unboosted flame}

\iffalse
\input{flame_table_1d.tex}
\fi

>>>>

To understand the time and length scales involved in flame
propagation, we do a 1D simulation of a laminar flame using our
microphysics.  Figure~\ref{fig:flame} shows the flame properties for a 
% \AssignTo{Kiran and Mike will remake with the 10/10 boosted flame}
He flame using the standard conductivities and our simple reaction
network.  This flame had a density of $2\times 10^6~\gcc$ and 
% \MarginPar{double check}
temperature of $5\times 10^7$~K.  We observe that this flame speed is
about $10^5~\cms$, the flame width is about 40~cm, and it
takes about 3~ms to settle into a sustained flame.  Note that this speed
is quite small compared to the speed estimated in
\citet{spitkovsky2002}.  We expect a multidimensional flame to
accelerate due to hydrodynamics interactions (wrinkling, turbulence
interactions, directed flows feeding fuel into the flame, ...).

\begin{figure*}[t]
\plottwo{flame.pdf}{speed.pdf}
\caption{\label{fig:flame} Time-evolution of the 10$\times$ boosted 1D laminar flame. The left plot shows temperature and nuclear energy generation profiles at 11 different time points, while the right plot shows flame propagation speed and flame thickness as functions of time.}
\end{figure*}

@@

Flame propagation rates from both the 1D laminar flames and full 2D simulations are given in Table \ref{table:flame_speeds}.
